Nirdizati: A Web-Based Tool for\\ Predictive Process Monitoring

### 2017-06-18 BPM17-demo-paper/paper.tex
modify arch pic
changed list of authors and URLs to deployed versions

\urldef{\mailsa}\path|{andriiro,f.m.maggi,marlon.dumas}@ut.ee, kerwin.jorbina@gmail.com|
\urldef{\mailsb}\path|{dfmchiara,ghidini}@fbk.eu|
\urldef{\mailsc}\path|{ilya.verenich,m.larosa,simon.raboczi}@qut.edu.au|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Andrii Rozumnyi\inst{1}  \and Chiara Di Francescomarino\inst{2} \and Chiara Ghidini\inst{2}  \and \\Fabrizio Maria Maggi\inst{1} \and Ilya Verenich\inst{3,1} \and Kerwin Jorbina\inst{1} \and Marcello La Rosa\inst{3} \and  Marlon Dumas\inst{1} \and Simon Raboczi\inst{3}\thanks{Author names are in alphabetical order}}

\institute{University of Tartu, Estonia\\
\mailsa
\and FBK IRST, Trento, Italy\\
\mailsb
\and Queensland University of Technology, Australia\\
\mailsc
}

@@

\keywords{Process Mining, Predictive Process Monitoring, Machine Learning}
\end{abstract}

@@

A screencast of Nirdizati's training and runtime components can be found at \url{https://youtu.be/hdfXMQTd4Qw}. The public release of Nirdizati is available at \url{http://nirdizati.com} and its source code has been released under the Lesser GNU Public License (L-GPL) at \url{http://github.com/nirdizati}.
\bibliographystyle{splncs03}
\bibliography{paper}

>>>>

\urldef{\mailsa}\path|{kerwin,andriiro,f.m.maggi,marlon.dumas}@ut.ee|
\urldef{\mailsb}\path|{dfmchiara,ghidini}@fbk.eu|
\urldef{\mailsc}\path|{ilya.verenich,m.larosa,simon.raboczi}@qut.edu.au|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Kerwin Jorbina\inst{1} \and Andrii Rozumnyi\inst{1} \and Ilya Verenich\inst{1,2}  \and Chiara Di Francescomarino\inst{3} \and  Marlon Dumas\inst{1}  \and Chiara Ghidini\inst{3}  \and Fabrizio Maria Maggi\inst{1} \and Marcello La Rosa\inst{3} \and Simon Raboczi\inst{3}}

\institute{University of Tartu, Estonia\\
\mailsa
\and Queensland University of Technology, Australia\\
\mailsc
\and FBK IRST, Trento, Italy\\
\mailsb
}

@@

\keywords{Predictive Process Monitoring, Machine Learning}
\end{abstract}

@@

A video demo of Nirdizati can be found at \url{https://youtu.be/hdfXMQTd4Qw}. A public release of Nirdizati Training and Nirdizati Runtime are available at \url{http://training.nirdizati.com} and \url{http://dashboard.nirdizati.com} respectively. The source code is available under the Lesser GNU Public License (LGPL) at \url{http://github.com/nirdizati}. 
\bibliographystyle{splncs03}
\bibliography{paper}
